Sophize Mathematics Library

### 2022-08-08 math_library/sophize_math.tex
Submission (with sources) to CICM

Another use case would be to understand the consequences of important conjectures like the Reimann hypothesis by creating two belief sets - one where the conjecture is true and one where it is false. The proof graphs would systematically store such conjectural knowledge which often gets lost especially when results from multiple conjectures are involved. Complexity theory is one such field where this need is quite apparent. Such conjectural knowledge knowledge can have practical applications too. For example, a lot of our information security systems utilize the knowledge developed with the conjectures $P \neq NP$.

>>>>

Another use case would be to understand the consequences of important conjectures like the Riemann hypothesis by creating two belief sets - one where the conjecture is true and one where it is false. The proof graphs would systematically store such conjectural knowledge which often gets lost especially when results from multiple conjectures are involved. Complexity theory is one such field where this need is quite apparent. Such conjectural knowledge knowledge can have practical applications too. For example, a lot of our information security systems utilize the knowledge developed with the conjectures $P \neq NP$.
